### 2016-09-18 image_setup.tex
minor
draf

The update script lines (3-4) checks for the \ac{URL} and \texttt{.zip} file that
should be downloaded. Lines (7-10) downloads the configuration files to \texttt{/tmp}
folder in the corresponding \ac{Raspi}. It also prints a warning in case of
errors and line (13) unzips the files to \texttt{/home/pi/}, the \ac{Raspi} home
directory. Existing files and directories are simply overwritten.
%while ignoring existing files and / or directories there.

@@

The Raspbian lite image should now be possible to use almost as if it had
been booted in a \ac{Raspi}. A major difference is that the testbed
administrator \ac{PC} is likely significantly faster than a \ac{Raspi}.
Hence, enabling updates, upgrades and installing new software packages
should be faster than in a \ac{Raspi}. Still updating and upgrading
the packages for the \ac{Raspi} might take some amount of time. To get
the upgraded system packages, it is necessary to run:

% Update system
\begin{lstlisting}[]
(chroot) # apt-get update
(chroot) # apt-get upgrade
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}

>>>>

The update script lines (3-4) specifies the \ac{URL} and \texttt{.zip} file that
should be downloaded. Lines (7-10) downloads the configuration files to \texttt{/tmp}
folder in the corresponding \ac{Raspi}. It also prints a warning in case of
errors and line (13) unzips the files to \texttt{/home/pi/}, the \ac{Raspi} home
directory. Existing files and directories are simply overwritten.
%while ignoring existing files and / or directories there.

@@

The Raspbian lite image should now be possible to use almost as if it had
been booted in a \ac{Raspi}. A major difference is that the testbed
administrator \ac{PC} is likely significantly faster than a \ac{Raspi}.
Hence, enabling updates, upgrades and installing new software packages
should be faster than in a \ac{Raspi}. Still updating and upgrading
the packages for the \ac{Raspi} might take some amount of time.
%To get the upgraded system packages, it is necessary to run:
To update the system package list, run the following command:

% Update system
\begin{lstlisting}[]
(chroot) # apt-get update
\end{lstlisting}
\FloatBarrier
\vspace{-5mm}
